---
title: "Plan"
output: html_document
date: "2025-04-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### The Ology Trio

Data set : https://www.kaggle.com/datasets/sanyacodes/movies-dataset-netflix-prime-video-disney
```{r}
library(tidyverse)
library(dplyr)
library(janitor)
streaming_data <- read_csv("MoviesOnStreamingPlatforms 2.csv") %>% clean_names()
glimpse(streaming_data) 
```

# What's In It?

 This dataset contains information on movies available across four major streaming platforms: Netflix, Prime Video, Disney+, and Hulu. It includes data points like: 

- Title 

- Genre(s) 

- Age Group Recommendations

- Rotten Tomatoes scores 

- Year of release 

- Platform availability flags (0 or 1 for each) 

- Type: A categorical indicator distinguishing the content as either a 'Movie' or a 'TV Show'.

This dataset is useful because it lets us look at and compare what each streaming service offers; like what kinds of movies they have, how good those movies are, and which genres are most common. We can also see patterns in ratings, find out which movies are only on one platform, and watch how their movie collections have changed over time. 

---

## Introduction to the Data 

Streaming platforms are now the go-to for watching movies and shows, and each one has its own unique library. With all the competition for content, it’s more important than ever to understand what sets these platforms apart — not just in what they have, but in the quality and variety of their offerings. This dataset gives us a snapshot of what’s available on Netflix, Prime Video, Disney+, and Hulu. By exploring the data, we can spot each platform’s strengths, see trends in genres and quality, and help people or companies make smarter choices when it comes to content.

---
```{r}


```

### Questions We Plan to Ask (and Graphs to Make) 

1. Which platform has the highest-rated content overall (based on Rotten Tomatoes scores)?

 Bar graph comparing average Rotten Tomatoes score for each platform
 
```{r}
highest_rated <- streaming_data %>% summarise(Highest=max(rotten_tomatoes, na.rm = TRUE))

highest_rated
```


Which platform has the highest-rated content overall (based on Rotten Tomatoes scores)?
Bar graph comparing average Rotten Tomatoes score for each platform
```{r}

```
 
How many titles are available on each platform?
Bar graph showing total number of titles per platform
```{r}
titles_available <- streaming_data %>% 
   summarise(
    Netflix = sum(netflix, na.rm = TRUE), #counting the number of 1s
    Hulu = sum(hulu, na.rm = TRUE),
    Disney = sum(disney, na.rm = TRUE),
    Prime = sum(prime_video, na.rm = TRUE)
  ) %>%
  pivot_longer(cols = everything(), names_to = "Platform", values_to = "Count") %>%
  ggplot(aes(x = Platform, y = Count, fill = Platform)) +
  geom_bar(stat = "identity") +
  labs(
    title = "Total Titles Available Per Platform",
    x = "Platform",
    y = "Number of Titles"
  )

titles_available
```

How has the number of titles released over time changed for each platform?
Line graph showing number of titles per release year, grouped by platform
```{r}
titles_over_time <- streaming_data %>%
  select(title, year, netflix, hulu, disney, prime_video) %>%
  pivot_longer(
    cols = c(netflix, hulu, disney, prime_video),
    names_to = "Platform",
    values_to = "Available"
  ) %>%
  filter(Available == 1, !is.na(year)) %>%  # Only keep titles available on a platform and with a known year
  group_by(year, Platform) %>%
  summarise(Count = n()) %>%
  ungroup()

ggplot(titles_over_time, aes(x = year, y = Count, color = Platform)) +
  geom_line() +
  labs(
    title = "Number of Titles Released Over Time by Platform",
    x = "Release Year",
    y = "Number of Titles",
    color = "Platform"
  ) 
```

Which platform has the most highly rated content (RT score > 90%)?
Bar chart showing count of high-rated titles per platform
```{r}

```

How do age ratings vary across platforms?
Grouped bar chart showing count of each age rating (e.g., PG, R) per platform
```{r}

```


Which platforms focus more on older vs. newer titles?
Histogram showing release years per platform
```{r}

```

How do average Rotten Tomatoes scores differ by age rating?
Boxplot or bar chart showing average score per age group
```{r}

```

How have average Rotten Tomatoes scores changed over time per platform?
Line graph of average score by year for each platform
```{r}


```

Which age ratings are underrepresented on each platform?
Heatmap or bar chart showing low-count age groups per platform
```{r}

```


```
 
 
 

2. How many titles are available on each platform?

```{r}
platform_counts <- streaming_data %>%
  summarise(
    Netflix = sum(netflix),
    Hulu = sum(hulu),
    Prime.Video = sum(prime_video),
    Disney. = sum(disney)
  ) %>%
  pivot_longer(cols = everything(), names_to = "Platform", values_to = "Title_Count")

platform_counts
```

```{r}

ggplot(platform_counts, aes(x = reorder(Platform, -Title_Count), y = Title_Count)) +
  geom_bar(stat = "identity", fill = "darkgreen") +
  labs(title = "Number of Titles per Platform", x = "Platform", y = "Title Count") +
  theme_minimal()


```

bar graph showing total number of titles per platform

3. How has the number of titles released over time changed for each platform?



 Line graph showing number of titles per release year, grouped by platform

4. Which platform has the most highly rated content (RT score > 90%)?
 Bar chart showing count of high-rated titles per platform
 
 
```{r}

highly_rated <- streaming_data %>% filter(rotten_tomatoes > 90)

hr <- highly_rated %>%
  summarise(
    Netflix = sum(netflix),
    Hulu = sum(hulu),
    Prime.Video = sum(prime_video),
    Disney. = sum(disney)
  ) %>%
  pivot_longer(cols = everything(), names_to = "Platform", values_to = "High_Rated_Count") %>%
  arrange(desc(High_Rated_Count))

hr

```

```{r}

ggplot(hr, aes(x = reorder(Platform, -High_Rated_Count), y = High_Rated_Count)) +
  geom_bar(stat = "identity", fill = "tomato") +
  labs(title = "Highly Rated Content (RT > 90%) per Platform",
       x = "Platform", y = "Number of Titles") +
  theme_minimal()


```




5. How do age ratings vary across platforms?
 Grouped bar chart showing count of each age rating (e.g., PG, R) per platform
 
```{r}
#platform_age <- streaming_data %>% filter(Age) %>% select(Netflix, Hulu, Disney., Prime.Video)

#platform_age


```
 
 
 

6. Which platforms focus more on older vs. newer titles?
 Histogram showing release years per platform


7. How do average Rotten Tomatoes scores differ by age rating?
 Boxplot or bar chart showing average score per age group
 
```{r}

```

 
 
 
8. How have average Rotten Tomatoes scores changed over time per platform?
 Line graph of average score by year for each platform
 

9. Which age ratings are underrepresented on each platform?
 Heatmap or bar chart showing low-count age groups per platform



